VOCC outline

### 2020-04-23 ms/ms.Rmd
# new figs out for knitting

```{r global-coefs-w-age, fig.cap="Overall coefficient estimates for model with mature as the intercept and two-way interactions with immature.", out.width="3in"}
include_graphics(here("ms", "figs", "supp-global-coefs-w-age.pdf"))
```

@@

```{r mat-residuals, fig.cap="Spatial residuals of mature biomass of each species in the trend-based model of biomass change predicted by environmental change.", out.width="7in"}
include_graphics(here("ms", "figs", "supp-mat-residuals.pdf"))
```

@@

```{r imm-residuals, fig.cap="Spatial residuals of immature biomass in the trend-based model of biomass change predicted by environmental change.", out.width="7in"}
include_graphics(here("ms", "figs", "supp-imm-residuals.pdf"))
```

>>>>

```{r global-coefs-w-age, fig.cap="Overall coefficient estimates for model with mature as the intercept and two-way interactions with immature.", out.width="3in"}
# include_graphics(here("ms", "figs", "supp-global-coefs-w-age.pdf"))
```

@@

```{r mat-residuals, fig.cap="Spatial residuals of mature biomass of each species in the trend-based model of biomass change predicted by environmental change.", out.width="7in"}
# include_graphics(here("ms", "figs", "supp-mat-residuals.pdf"))
```

@@

```{r imm-residuals, fig.cap="Spatial residuals of immature biomass in the trend-based model of biomass change predicted by environmental change.", out.width="7in"}
# include_graphics(here("ms", "figs", "supp-imm-residuals.pdf"))
```
